\chapter{Future work}

POOP-SNOOP had many flaws of design. To continue to study the importance of ``juicy" design in citizen science applications it would be pertinent to fix problems of understanding for the users. Instead of introducing so much science originally, the game should be modified such that players can immediately begin playing and interacting with the puzzle. When players begin POOP-SNOOP, they should learn how to solve the puzzle first, then begin to learn the science behind it, if at all. There was very little positive feedback about the scientific portion of the tutorial. Because of the difficulty people had with the tutorial, it should be modified.

Immediate feedback in POOP-SNOOP did not engage users as much as intended. Iterative design would have yieled changes in my design with respect to how the user responds to input. Though this work makes the point of important with every user input and a corresponding output. When players begin moving row/columns and adjusting the solution, there should be feedback; not only when the row/columns are released.

The implementation of ``juicy" positive emotional feedback should be reassessed for future work. Users were too confused be encouraged from bombastic background animations. Work should be done iterating the scope and amount feedback users prefer.

Sound is such an important part of ``juicy" design that it could be just as important as visual feedback of any kind. Sound is especially important because of users senstivity in that aspect as well. Well-crafted tones, effects, and background music could be unparalleled in terms of engagement, unfortunately POOP-SNOOP did not explore sound.

Even the ``juiceless" version of POOP-SNOOP had positive responses to the user interface. Participants praised the ``clean interface" which brings up the question: does a clean interface give the feeling of professionality and seriousness? Is that influencial in a citizen science application? POOP-SNOOP does not attempt to answer these questions.

\section{Long-term Engagement}

POOP-SNOOP only took the tutorial and introductory level into consideration. There is serious value in understanding ``juicy" design's role in long-term engagement, especially in the field of citizen science.
